5/16
Write modified records.

Pretty up record.toString() 
	sort fields
	indent subfields (5/17)
	filter fields displayed (std set including the fields I'm dealing with; option to see others) (5/17)

Add subfields indicating where the info came from (5/20)
Stats/display what rules are being used, how often, stuff like that

Conceptualize new fields to indicate status: 1-5 done/not done/whatever

Partition input by finished/not? Or just handle by filters? 
Stats thereof?

Mappings from sets of variants/typos to keywords.
    Tool mostly built (5/17)

5/18
Build mapping from {variants} -> keywords (i.e. {videocassete, vidoecassette, videocasette} -> videocassette
    automagically!?

Rules:
    Write 96x records as: =961  \\$a300$b1$ca$d1$e1$fP12M$gtotal$iapproximate time$jcorrect (5/20)
    Record which RS:rule gleaned the info when writing the 96x records (5/21)

Processing:
    Check if already applied before trying to apply rules again
    Generate stats
        for each task
            how many finished
            how many not (%?)
                create lists of relevant fields (StringList)
                    sorted
                    counted
    Set input/output directories and write them locally

GUI
    Testing
        for a rule
            how many matches
        for a set of rules (rule set (RS)) e.g. duration.rs how many matches, how many misses
        select task/RS
        given a RS, glean fields used, display those (as an option)
    Processing

5/27 -- next steps
Review/fix RuleSet, RuleReader, and the tangle of Globals.setRulething, Rule.setRuleSet... etc
Check that the simple Duration rules work (yes! they do!)
    make the RuleDialog thing pop up over to the right...
Test the pattern-based (regex) rules (5/30)

jar and writing to the um... master path file thingee from jar...
Here's a clue:
        URL bar = Rule.class.getResource("resources/fileInfo.txt");
        System.out.println("bar = " + bar.getPath());
Maybe??

5/30
Write code to handle multiple fields in the condition part (all ors) -- (5/31, but not tested extensively!)
Write code for #.#:1 (6/5)

*****************************************************************************
BIG PICTURE:

Format (960)
    Group 1 done 6/5
    Group 2 done 6/5
    Group 3 maybe done 6/6
    Group 4 done 6/8

Duration (961)
    Group 1 done 5/19
    Group 2

Color (962)
    Group 1 done 5/24
    Group 2 done 6/6        only applies the *first* matching rule, so order is important!

Sound (963) -- these only apply the *first* matching rule, so order is important!
    Group 1 done 6/2
    Group 2 done 6/4
    Group 3 done 6/3

Aspect Ratio (964)
    Group 1 done 5/31
    Group 2 done 6/5

*****************************************************************************

Argh! As far as I can tell, I can write to /Users/levenick/kelley/olddata/output/someFile.mrc, but when I try it
to /Users/levenick/kelley/marc/build/classes/org/marc4j/rules/resources/data/output/foo.mrc, it doesn't write... :((((( 
...but no Exceptions... just nothing...
Gee!  Look at the "build" in that second pathname... curious, no?
Gah! Gah! Gah!
(solved by working from/with the directory specified in fileinfo.txt)

5/31
Need to figure out how to package so someone else can run it... (kinda done 6/2)

6/3
Allow user to specify output file (done)
Write output file to input so they can read it in again (done 6/3)
Run *all* the rulesets against the input...
Quit displaying the rules when switch rulesets (done 6/3)
Close dialog when they chose a rule (done 6/3)

6/4
Replace field, subfield in Rule with, uh... FieldSpecifier
                                wrote display ruleset
                                wrote commas to tabs (so commas in the input work!)
Add debug controls! (done 6/5)

6/5
Need to make an option to match all rules, or match first... gah! (done 6/5)
    Plainly, Format1.csv is meant to match *all* the rules, whereas Sound and Color should stop once one matches...

6/6
Write code to select a rule and display (the first n) records that match it (like for R14 in Format3 which may or may not work...
Read/review code, add comments and instructions for how to do things like Format4 (which is trivial, but not obvious!)

6/7
Finish with Format4... test 1/2, 12, and 3 3/4 in... handle new rules (maybe add wholeUnit to unit?) (done 6/8)

6/8
Close the diagnostic window after it starts!! (done 6/8)
Attempt to apply a second ruleset to even before fails... wonder if there's a blank line or something... gah! (Fixed 6/9)

6/10 
Added # in the actions to create a second 96x field with the remaining actions...

6/11
Add output for $c for control fields (done 6/11)

6/22
Working with Duration2
    seems like R4 should have also match the number of items, no??
        i.e. instead of 
            \([ ]*(approx\.)[ ]*\d+[ ]*(min|minute)(|s)(|\.)[ ]*ea\.\)
        should be (?)
            \d+([ ]*)[a-zA-Z -]*.*\([ ]*(approx\.)[ ]*\d+[ ]*(min|minute)(|s)(|\.)[ ]*ea\.\)
    seems like R8 should have keywords to say just 2 parts?
            and R9
            an R10

    partMinutes and partNumber pseudocode
        numberParts = first int in matched data
        partMinutes = second?
        for (int i=1; i<=numberParts {
            generate another 961 field (which means it has to be in the loop out in Rule!)
    Um... how to do this nicely (since need to have the part number inside action)... maybe add a param to createAndAddNewField, which tells which part
number, and just ignore it if we don't have a part number to generate?  It's just so ugly!  Sigh...
    
6/23
Solved parts by storing the number of repetitions in Globals...
    added totalMinutes, and totalHours to the list of output specials

2,000 mins kills it... since the 0... um... don't know!! (done 6/24)

In the process of modularizing reading/setting the ruleset...  (done 6/24)
    look at doItAll...
    need to add parameter to readRuleSet, so it's reuseable... (done 6/24)

6/24
Need to add rest of Duration2
    approx...
    ca... (for hours and etc?) (done 6/26)
    hr, min, sec !! (done 6/24)

Look at this example:
	$bdigital, WMV file, si. (some talking sequences), col. tinted with b&w segments
    should be silent with some sound?

Handle (12, 14, 45 min) (done 6/24)

6/27
Think about GUI for no 96x
When using Globals.count, make a list of which field??

Field 961    (fixed 6/25)
	$a008
	$b1
	$c18
	$fP00H00M00S
	$gtotal
	$jcorrect
	$r/Users/levenick/kelley/data/rules/Duration.csv R0
instead of 
Field 961   
	$a008
	$b1
	$c18-20
	$d1
	$e1
	$fP12M
	$gtotal
	$jcorrect

Field 961   
	$a300
	$b1
	$ca
	$d1
	$e1
	$f12M
	$gtotal
	$jcorrect
	$r/Users/levenick/kelley/data/rules/Duration2.csv R3
instead of
Field 961   
	$a300
	$b1
	$ca
	$d1
	$e1
	$fP12M
	$gtotal
	$iapproximate time
	$jcorrect

make it 2 decimals! (fixed 6/25)
        $g2.3:1 
	$h(2.35:1)
	$r/Users/levenick/kelley/data/rules/Aspect.csv R0


Sound3 is all wrong; er... it should not be 999 since it is supposed to do various of them... so need a different mechanism to avoid the ^ thang... (fixed 6/25)

I don't find: (fixed 6/25)

Field 960   
	$a538
	$b1
	$ca
	$d1
	$e3
	$fvideo
	$jWindows media
	$kWindows Media
in 42265014

Sound2 is seriously broken/incomplete!!  (fixed 6/25)
I generate:
Field 963   
	$a300
	$b1
	$cb
	$d1
	$e1
	$gprimary
	$fsound
	$gsecondary
	$ksi. (some talking sequences
	$r/Users/levenick/kelley/data/rules/Sound2.csv R2
...and the $k field is already in use!

Need to handle multiple 007 fields and not mix (fixed 6/25)
Field 007 cr cna||||||||
Field 007 vz mzazu|
...to get video reel!!

I don't think special650 works... :(
Perhaps it should be getVariableFields
                                     | ... or is it just the one?
6/26
Check partHours... still a stub? (Fixed 6/26)

Write code to count how many records do not end up with 96x (and print, or something). (done 6/26)